5 slides to convince you that it's endogenous TFP

### 2018-02-02 Latex/Basu_propositions/propositions.tex
another update to basu presentation
updated the presentation once more with another reference

Theoretical evidence
\begin{itemize}
\item Brynjolfsson, e.g. in Bloom et al. (2014): theory of IT as a GPT changing management practices.
\item Mokyr (1990):  an economic history account of how GPTs (electricity, computers) change the organization of production as a whole, so it's not just the firm's individual use of them that matters, but that of the economy as a whole.
\item Romer (1986): a production function with spillovers from human capital.
\end{itemize}

Empirical evidence
\begin{itemize}
\item Stiroh (2002 AER): industry-level data show that productivity gains from IT are not confined to industries producing IT.
\item Oliner \& Sichel (2000 JEP): growth accounting.
\item Black \& Lynch (2004, EJ), Doms, Dunn \& Troske (1997 QJE): plant-level data.
\end{itemize}

>>>>

Theoretical evidence
\begin{itemize}
\item Whelan (2001): a two-sector model with IT relative prices.
\item Brynjolfsson, e.g. in Bloom et al. (2014): theory of IT as a GPT changing management practices.
\item Mokyr (1990):  an economic history account of how GPTs (electricity, computers) change the \textbf{organization} of production $\rightarrow$ neither use, nor output value of IT, but \textbf{indirect} effect
\item Romer (1986): a production function with spillovers from human capital.
\end{itemize}

Empirical evidence
\begin{itemize}
\item Basu, Fernald, Oulton \& Srinivasan (2004 Macro Annuals)
\item Stiroh (2002 AER): industry-level data show that productivity gains from IT are not confined to industries producing IT.
\item Oliner \& Sichel (2000 JEP): growth accounting.
\item Black \& Lynch (2004 EJ), Doms, Dunn \& Troske (1997 QJE): plant-level data.
\end{itemize}
